NFL Draft Analysis

### 2020-05-11 draft_analysis.Rmd
Only evaluate the skill positions for the ML problem

# add year drafted to each observation, and filter out the defensive players.
df_2020 <- df_2020 %>%
  mutate(year = year) %>%
  filter(Pos == "QB" | Pos == "WR" | Pos == "RB" | Pos == "G" | Pos == "T")

@@

```{r off_roty}
off_df <- master_df %>%
  mutate(roty = ifelse(Player %in% roty_df$Player, "Yes", "No")) %>%
  filter(Pos == "QB" | Pos == "WR" | Pos == "RB" | Pos == "G" | Pos == "T")

@@

The summaries tell us how much influence each variable had on the model. It was interesting to see that position had such little influence in predicting the model. What is even more interesting is that the team the player was drafted to seemed to influence the model more than the pick number itself! Before I had trained the model, I expected pick, position, and then team to have relative influence in that order!

@@

Now let's get the top 10 players that the model is most certain will be the Offensive Rookie of the Year

@@

top5_roty <- df_2020 %>%
  top_n(5, Yes)

head(top5_roty)
```

Joe Burrow is our model's top prediction to win the MVP!!!

>>>>

# add year drafted to each observation, and filter out the defensive players.
df_2020 <- df_2020 %>%
  mutate(year = year) %>%
  filter(Pos == "QB" | Pos == "WR" | Pos == "RB")

@@

```{r off_roty}
off_df <- master_df %>%
  mutate(roty = ifelse(Player %in% roty_df$Player, "Yes", "No")) %>%
  filter(Pos == "QB" | Pos == "WR" | Pos == "RB")

@@

The summaries tell us how much influence each variable had on the model. It was interesting to see that position had such absolutely zero influence in predicting the model. This tells us that quarterbacks, wide receivers, or running backs do not have a leg up on each other for the MVP award!

What is even more interesting is that the team the player was drafted to seemed to influence the model more than the pick number itself! Before I had trained the model, I expected pick, position, and then team to have relative influence in that order!

@@

Now let's get the top 7 players that the model is most certain will be the Offensive Rookie of the Year

@@

top10_roty <- df_2020 %>%
  top_n(10, Yes)

top10_roty
```

Joe Burrow is our model's top prediction to win the MVP!!! We also see that Cam Akers, Tua, Henry Ruggs III, Jerry Jeudy, CeDee Lamb, and Justin Jefferson also appear in the top 10. All of these players currently have the highest odds to win the the Offensive MVP according to OddsShark.
